\Large Inferential Analysis of the Supreme Court Citation Network

### 2018-03-11 Tex/paper.tex
added holdout experiment results to tex

\begin{table}[ht]
\centering
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
  \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5499 & (0.5384, 0.5619) & 0.8605 & (0.8526, 0.8666) \\ 
  recall & 0.0827 & (0.0811, 0.0843) & 0.5858 & (0.5817, 0.5891) \\ 
  F1 score & 0.1438 & (0.141, 0.1463) & 0.6971 & (0.6941, 0.7008) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models, over ten 80/20 train/test splits.}
\label{tab:prediction}
\end{table}

We see from Table \ref{tab:prediction} that, based on all three measures, the predictive performance of the model improves dramatically from adding the network dependence terms. The recall of the full model is particularly impressive, indicating that it recovers over half of the actual citations in the test set. This provides clear evidence that the full model, which includes covariates and network dependence terms, represents a more accurate and complete model of the process of citation formation in US Supreme Court opinions.

>>>>

\begin{table}[H]
\centering
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5582 & (0.5509, 0.5751) & 0.8678 & (0.865, 0.8721) \\ 
  recall & 0.0995 & (0.0953, 0.1043) & 0.5937 & (0.588, 0.6027) \\ 
  F1 score & 0.1688 & (0.163, 0.1766) & 0.7051 & (0.7009, 0.7117) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with linear trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.8827 & (0.878, 0.8876) & 0.8672 & (0.8629, 0.8731) \\ 
  recall & 0.5316 & (0.5255, 0.5408) & 0.5939 & (0.5872, 0.6008) \\ 
  F1 score & 0.6635 & (0.6594, 0.6709) & 0.705 & (0.7008, 0.7118) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quadratic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quadratic}
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.8745 & (0.8718, 0.8769) & 0.8667 & (0.8649, 0.8684) \\ 
  recall & 0.5732 & (0.5693, 0.5783) & 0.5949 & (0.5902, 0.5981) \\ 
  F1 score & 0.6925 & (0.6892, 0.6969) & 0.7056 & (0.7025, 0.7083) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with cubic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_cubic}
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.8769 & (0.8738, 0.881) & 0.8687 & (0.8646, 0.8718) \\ 
  recall & 0.583 & (0.5754, 0.5896) & 0.5956 & (0.5895, 0.6008) \\ 
  F1 score & 0.7004 & (0.6946, 0.7042) & 0.7067 & (0.7018, 0.7098) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quartic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quartic}
\end{table}

We see from Table \ref{tab:prediction_linear} that, based on all three measures, the predictive performance of the model improves dramatically from adding the network dependence terms. The recall of the full model is particularly impressive, indicating that it recovers over half of the actual citations in the test set. This provides clear evidence that the full model, which includes covariates and network dependence terms, represents a more accurate and complete model of the process of citation formation in US Supreme Court opinions.
